---
title: "Analyzing the trend over time"
author: "Diksha Shrestha"
date: "4/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(dplyr)

```

```{r}
library(ggplot2)
library(tidyverse)
```


#finding the average sale price across different cities using group_by function
```{r}
New_Data = read.csv("New_Data.csv")
Trend <- New_Data %>%
  dplyr::select(City, Year, Sale_Price) %>%
  group_by(City, Year) %>%
  summarise(Average_Sale_Price = mean(Sale_Price)) 


View(Trend)

  
```

#Preprocessing the Average Sale Price in Thousands
```{r}

Trend$Avg_Sale_Price <- (Trend$Average_Sale_Price)/1000
Trend
```
#Extracting the trend file
```{r}
write.csv(Trend,"~/STA 518/Final_Project/Trend.csv", row.names = TRUE)
```


#Line Graph of all the cities showing the average sale price.
```{r}

ggplot(Trend, aes(x=Year, y = Avg_Sale_Price, colour = City)) + 
  geom_line()+
  labs(y = 'Avg Sale Price(In Thousands)', title = 'Average Sale Price across cities')

```
#Summary of data
```{r}
Trend %>%
  summary(Average_Sale_Price)
```

#Line Graph of 4 cities except Queens
```{r}
Four_Cities <- Trend %>%
  filter(City != "Queens")

Four_Cities
```
#Extracting the Four City file
```{r}
write.csv(Four_Cities,"~/STA 518/Final_Project/Four_Cities.csv", row.names = TRUE)
```

#Line Graph of four_cities showing the average sale price.
```{r}
ggplot(Four_Cities, aes(x = Year, y = Avg_Sale_Price, colour = City))+
  geom_line()+
  labs(y = 'Avg Sale Price(In Thousands)', title = 'Average Sale Price of four cities')

```

#Summary of data
```{r}
Four_Cities %>%
  summary(Average_Sale_Price)
```




