---
title: "Bootstrap"
author: "Diksha Shrestha"
date: "4/14/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
avocado <- read.csv("Avo.csv")
avocado
```


```{r}
avocado = avocado[!(is.na(avocado$AveragePrice) | avocado$AveragePrice == "0"),]
```

```{r}
avocado = avocado[!(is.na(avocado$TotalVolume) | avocado$TotalVolume == "0"),]
```


```{r}
library(dplyr)
```

```{r}
avocado %>%
  mutate(Date = as.Date(Date, "'%m,%d,%Y"))

avocado
```



```{r}
library(boot)

avo <- function(avocado, i){
 d2 <- avocado[i,] 
 return(cor(d2$AveragePrice, d2$TotalVolume))
}

```

The above function uses the dataset from the avocado and i refers to the vector which means that the rows from the avocado dataset will be chosen to perform the bootstrap sample.

```{r}
set.seed(1)
bootstrap_correlation <- boot(avocado,avo,R=10000)
```

The set seed function is used to select the same random number every time we run the same code chunk to ensure we get the same result.


```{r}
bootstrap_correlation
```
From the above code, we can see that the original correlation between the average price and the total volume is **-0.533** and the standard error between them is **0.061**. This negative correlation shows that the both the variable moves in different direction ad has a negative relationship.


```{r}
summary(bootstrap_correlation)
```
The above code chunk provides the summary of the correlation.

```{r}
range(bootstrap_correlation$t)
```

Through the range bootstrap code, we can find the range of the correlation co-efficient which is between **-0.739** to **-0.306**.

```{r}
mean(bootstrap_correlation$t)
```
We can see that the mean of the coorelation coefficient is negative which is **-0.533**.

```{r}
sd(bootstrap_correlation$t)
```

We can also know the standard deviation which is **0.0613**.



```{r}
boot.ci(boot.out=bootstrap_correlation,type=c('norm','basic','perc','bca'))
```
The above function shows the confidence interval of the normal, basic, percentile and bca distribution.



