---
title: "Comparing_Residential_and_Commercial_Unit"
author: "Diksha Shrestha"
date: "4/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Selecting the Residential and Commercial Units
```{r}
Unit <- New_Data %>%
  dplyr::select(Residential_Units, Commercial_Units, Year, Borough, City)%>%
  group_by(Year, City) 

Unit
```


#Selecting the Residential Units Only
```{r}
Residential <- New_Data %>%
  select(Residential_Units, Year, Borough, City) %>%
  group_by(City, Year)

Residential
```


#Calculating the total number of Residential Units
```{r}
Residential_Sum <- New_Data %>%
  dplyr::select(Residential_Units, Year, Borough, City) %>%
  group_by(City, Year)%>%
  summarise(Sum_Residential = sum(Residential_Units))
 

Residential_Sum
```

#Extracting the file 
```{r}

write.csv(Residential_Sum,"~/STA 518/Final_Project/Residential_Sum.csv", row.names = TRUE)
```

#Bar Graph showing the number of  Residential Unit
```{r}
ggplot(Residential_Sum, aes(x = Year, y = Sum_Residential))+
  geom_bar(stat = "identity", fill = "aquamarine3")+
  labs(y = 'Residential Unit ', title = "Number of Residential Unit sold over the Year")
```





#Selecting the Commercial Units Only
```{r}
Commercial <- New_Data %>%
  dplyr::select(Commercial_Units, City, Year, Borough) %>%
  group_by(Year, City) 

Commercial
```
#Calculating the total sum of Commercial Units
```{r}
Commercial_Sum <- New_Data %>%
  dplyr::select(Commercial_Units, Year, City, Borough) %>%
  group_by(City, Year)%>%
  summarise(Sum_Commercial = sum(Commercial_Units))

Commercial_Sum
```
#Extracting the file 
```{r}

write.csv(Commercial_Sum,"~/STA 518/Final_Project/Commercial_Sum.csv", row.names = TRUE)
```

#BarGraph showing the number of commercial units
```{r}
ggplot(Commercial_Sum, aes(x = Year, y = Sum_Commercial))+
  geom_bar(stat = "identity", fill = "deepskyblue3")+
  labs(y = ' Commercial Unit', title = "Number of Commercial Unit sold over the year")
```




